Computing solution space properties by generic programming tensor networks \thanks{\funding{...}}

### 2022-03-21 paper/paper.tex

    \begin{subfigure}[t]{\textwidth}
        \centering
        %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.1-n10000.pdf}
        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.05-n10000.pdf}
        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
        \caption{Nine King's graphs of size $20\times 20$, $0.8$ filling.}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.1-n10000.pdf}
        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.05-n10000.pdf}
        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
        \caption{Nine random three regular graphs of size $110$.}
    \end{subfigure}

>>>>

    % \begin{subfigure}[t]{\textwidth}
    %     \centering
    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.1-n10000.pdf}
    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.05-n10000.pdf}
    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
    %     \caption{Nine King's graphs of size $20\times 20$, $0.8$ filling.}
    % \end{subfigure}
    % \begin{subfigure}[t]{\textwidth}
    %     \centering
    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.1-n10000.pdf}
    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.05-n10000.pdf}
    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
    %     \caption{Nine random three regular graphs of size $110$.}
    % \end{subfigure}
    \includegraphics[width=\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/fig6.pdf}
